%-------------------------
% Resume in Latex
% Author : Sayali Patkar
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[pdftex]{hyperref}
\usepackage{fancyhdr}
% for symbols
\usepackage{graphicx,xcolor,fontawesome}
\usepackage{csquotes}
\usepackage{ragged2e}



\pagestyle{fancy}
% clear all header and footer fields
\fancyfoot{}
\fancyhf{} 
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
   \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

\newcommand{\educationSubheading}[4]{
  \vspace{-1pt}\item
	%Rubber spacing
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} &  \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{\justify #2}\vspace{-4pt}}
%for hollow circular bullets
\renewcommand{\labelitemii}{$\circ$}

\newcommand{\educationSubHeadingListStart}{\renewcommand\labelitemi{\raisebox{1.50ex}{$\bullet$}}\begin{itemize}[leftmargin=*]}
\newcommand{\educationSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\newcommand{\projectSubHeadingListStart}{\renewcommand\labelitemi{\raisebox{1.50ex}{$\bullet$}} \begin{itemize}[leftmargin=*]}
\newcommand{\projectSubHeadingListEnd}{\end{itemize}}
\newcommand{\projectSubheading}[3]{
  	\vspace{-1pt}\item{
		\begin{tabular}{p{0.4\linewidth}p{0.4\linewidth}p{0.2\linewidth}}
			
      		  \textbf{#1} & \textit{#2} & \raggedleft\textit{\small#3}\\
			
    		\end{tabular}}
	\vspace{-5pt}
}

\newcommand{\skillsSubHeadingListStart}{\renewcommand\labelitemi{\raisebox{0.00ex}{$\bullet$}} \begin{itemize}[leftmargin=*]}
\newcommand{\skillsSubHeadingListEnd}{\end{itemize}}

\newcommand\mypound{\scalebox{0.8}{\raisebox{0.4ex}{\#}}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING-----------------
\centering
	{\fontsize{20}{30}\selectfont\bfseries Sayali Patkar\par}
	\textcolor{NavyBlue}{\faMapMarker}\space \textit{XXXXXXXX XX, Kiel, Germany, 24149}
	\vspace{-2mm}
	\begin{table*}[ht]
		\begin{tabular}{p{0.25\linewidth}p{0.25\linewidth}p{0.25\linewidth}p{0.4\linewidth}}
			\textcolor{NavyBlue}{\faMobile}\space \textit{X-XXXXXXXX} & \textcolor{NavyBlue}		{\faLinkedin}\space\space \href{https://www.linkedin.com/in/sayali-patkar-515aba152/}{\textit{LinkedIn : Sayali}} & \textcolor{NavyBlue}{\faGithub}\space\space \href{https://github.com/SayaliPatkar}{\textit{Github : SayaliPatkar}} & 	\textcolor{NavyBlue}{\faEnvelope}\space \textit{xx.xxxx@gmail.com}\\
		\end{tabular}
	\end{table*}
\vspace{-7mm}
%-----------EDUCATION-----------------
\section{Education}
  \educationSubHeadingListStart
	\educationSubheading
      {Fachhochschule Kiel}{Kiel, Deutschland}
      {Masters Information Engineering (Intelligent Systems);  Grade: 1.70}{Sept. 2016 -- Present}
    \educationSubheading
      {Watumull Institute affiliated with Mumbai University}{Mumbai, India}
      {Bachelor of Engineering in Electronics and Telecommunication;  Grade: 2.30}{Jul. 2009 -- May. 2013}
  \educationSubHeadingListEnd


%-----------ACADEMIC PROJECTS-----------------
\section{Academic Projects}
 	\projectSubHeadingListStart
	
	\projectSubheading
      {Master Project}{Fachhochschule Kiel}{Apr. 2018 -- Present}
	\vspace{-20pt}
	\resumeItemListStart
      	\resumeItem{Convolutional Neural Networks}
          	{worked on Phillips Research's \enquote{Biomedical Joint Detection Project} written with Python and TensorFlow using UNET CNN}
       	\resumeItem{Literature Suvey}
          {studied various traditional as well as state-of-the-art loss functions and their application and incorporated them in existing code}
		\resumeItem{Implementation and Analysis}
          {developed logic for calculation and visualization performance measuring metrics and compared different results}
	\resumeItemListEnd

	\projectSubheading
	{Pattern Recognition} 	{CAU, Kiel}	{Sept. 2017 -- Feb. 2018}
	\vspace{-20pt}
	\resumeItemListStart
        \resumeItem{Probability Calculus}
          {studied theoretical aspects like Maximum-Likelihood Estimation, K-nearest neighbors etc. that form basis of many ML algorithms and programmed applications demonstrating their practical usage}
        \resumeItem{Image Processing}
          {studied and gained hands on experience on image processing using MATLAB}
      \resumeItemListEnd

	\projectSubheading
	{Sentiment Analyzer}{Fachhochschule Kiel}{Mar. 2017 -- Jul. 2017}
	\vspace{-20pt}
	\resumeItemListStart
        \resumeItem{Natural Language Processing}
          {studied basics of NLP and sentiment analysis}
        \resumeItem{Full Stack Development}
          {developed fully functional C\mypound\space application performing sentiment analysis using Bing API and AFINN library}
      \resumeItemListEnd

	\projectSubheading
	{BuzzBeeper - TV Series Tracker}{Fachhochschule Kiel}{Sept. 2016 -- Feb. 2017}
	\vspace{-20pt}
	\resumeItemListStart
        \resumeItem{Leadership}
          {lead a team of 5 to develop full-stack web application using node.js, angular.js and web-sockets}
      \resumeItemListEnd

	\projectSubheading
	{Bachelors Project}{Mumbai University}{Jan. 2013 -- May. 2013}
	\vspace{-20pt}
	\resumeItemListStart
        \resumeItem{Wireless Sensor Network with Siemens}
          {as a trainee at Siemens designed and developed a sensor network that communicates with centralized micro controller using ZigBee wireless protocol}
      \resumeItemListEnd

 	\projectSubHeadingListEnd


%-----------INDUSTRIAL EXPERIENCE-----------------
\section{Industrial Expericence}
 	\projectSubHeadingListStart
	\projectSubheading
      {Ergovia GmbH, Kiel}{Part-time Software Developer }{Apr. 2017 - Jan. 2018}
\vspace{-20pt}
      \resumeItemListStart
        \resumeItem{Connection Pool Migration}
          {conducted research on connection pool options which can support massive data transfer and migrated from C3PO to Hikari CP}
        \resumeItem{Java 8 and Spring}
          {migrated outdated application to Spring-boot and Java-8 application that uses REST-API}
      \resumeItemListEnd

    	\projectSubheading
      {Capgemini India Pvt. Ltd.}{Associate Consultant }{Dec. 2013 - Aug. 2016}
\vspace{-20pt}
      \resumeItemListStart
        \resumeItem{Quick Learning}
          {worked on various projects that required quick grasp on everchanging technical requirements like spring-integration, spring-security, mocking and unit testing, server configurations and scripting}
        \resumeItem{Agile Development}
          {worked on HSBC's banking and insurance projects that followed Agile Development Model}
 	\resumeItem{Work Experience in Multi-city Team}
          {worked in multi-city teams on tight development and testing schedules}
	\resumeItem{Client Handling and Communication}
          {communicated with client on regular basis to understand entity specific requirements, defect resolutions and code deployments}
      \resumeItemListEnd

  \projectSubHeadingListEnd

%--------PROGRAMMING SKILLS------------
\section{Technical Skills}
  	\skillsSubHeadingListStart
		\item{\textbf{Languages}{: Python, Java, MATLAB, Javascript, C\mypound, SQL}}
		\item{\textbf{Libraries / Technologies}{: scikit-learn, TensorFlow, OpenCV, AWS, IBM Websphere}}
		\item{\textbf{Relevant Coursework}{: Neural Networks, Cognitive Consulting, Requirement Engineering, Pattern Recognition, Advanced Application Systems Development }}
		\item{\textbf{Publication}{:  \href{https://www.yumpu.com/en/document/view/43408325/wireless-sensor-network-using-zigbee-irnet-explore}{Wireless Sensor Networks using ZigBee : IRNET International Conference, March 2013 }}}

 \skillsSubHeadingListEnd


%-------------------------------------------
\end{document}